Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added the appendix about sharing work throughout the project.

\newpage
\appendix[Team Member Contributions]
Kenneth Lee did A, B, C.  Kyle Morgan did X, Y, Z.
\end{document}

>>>>

\newpage
\appendix[Team Member Contributions]
{\bf Kenneth Lee} was responsible for load-balancing schemes in
both design and implementation.  He was also in charge of system
integration and testing of the final applications on the appropriate
hardware devices.  Kenneth was also in charge of deep analysis and
explanation of result data.

{\bf Kyle Morgan} was in charge of kernel design and implementation.
In addition, he was also in charge of result compilation and 
preliminary analysis.  Kyle was also responsible for background readings
in both GPGPU computation in general, as well as specifics in terms of
both GPU architecture and the OpenCL framework.

\end{document}
